Structured Versus Decorated Cospans

### 2021-01-22 cospans_arxiv_1.tex
first arXiv version (polished remarks after Theorem 3.2)

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/21

@@

In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the involved structures. In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}

%Notice that in the above proof, when we compose two structured cospans, namely two horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.Thus in fact the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F\colon \A\to\SMC$ factors through the 2-category of categories with finite coproducts.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/22 - first arXiv version

@@

In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the structures involved. In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}

In fact, a careful examination of the proof reveals that the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F \maps \A \to \SMC$ factors through the 2-category $\mathbf{Cocart}$ of cocartesian monoidal categories.   The reason is that when we compose two structured cospans as in \cref{eq:pushoutissum}, the apex of the composite cospan ends up being a sum in the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.  However, in the interesting examples so far, when $F$ factors through $\mathbf{Cocart}$ it also factors through $\Rex$.
